---
title: "Using SummaryStats and RBD"
author: "Fred Kaesmann"
date: "May 9, 2019"
output: pdf_document
---

# What is SummaryPack

SummaryPack is a set of functions developed to assist the analysis of
assigned homework and project from MAT 342 Spring 2019 

# SummaryStats()


## To do a t.test on a single set of observations
```{r SummaryStats, eval=FALSE}
SummaryStats(observations)
```

## To do a two sample t.test on a set of observations

In this case, treatments has to be two factors
```{r, eval=FALSE}
SummaryStats(observations, treatments)
```
 

## To do a one way ANOVA 
It's the same as above
except in this case treatments has to have three or more factors
```{r, eval=FALSE}
SummaryStats(observations, treatments)
```


## For nonparametric data
If the Kruskal-Wallis test is significant, this will run Dunns test
```{r, eval=FALSE}
SummaryStats(observations, treatments, post.hoc = "Dunn", is.nonparametric = TRUE)
```

# RBD
## For the projects requiring two way ANOVAs
In this case, treatments should have three or more factors
```{r RBD, eval=FALSE}
RBD(observations, treatments, block)
```



